\documentclass[]{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}

\hypersetup{breaklinks=true,%
pagecolor=white,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}

\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.4}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}
\newcommand{\contactnumber}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}


\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{resume_header}
\name{Alex Statham}
\program{Computer science and AI}
\contact{alex.staham1998@gmail.com}
\contactnumber{+447490973388         astatham.com}     
\end{resume_header}

\begin{resume_section}{About Me}
  \begin{nospacetabbing}

  \textbf{Technical Skills}  \= Python, Java, Unix, GO, mysql, C#,  \LaTeX\\*
  \textbf{Interests} \> Machine learning,  Data analytics and visualisation,  Web scraping, Automation \\*
  \end{nospacetabbing}

\end{resume_section}

\begin{resume_section}{Work Experience}
	\begin{resume_employer}{Waitrose}{Multi-trained partner}{(October 2015 - May 2018)}{}
    \item Cross-trained to other roles to improve flexibility whilst showing the ability to quickly learn new skills.
    \item Interacted with customers to bring high quality customer service.
    \item Worked in small teams in high pressure situations to complete tasks to a high standard.
  \end{resume_employer}
  
  \begin{resume_employer}{Upwork}{Freelancer specialising in data science}{(November 2018 - Current)}{}
    \item Worked with clients to bring robust and reliable software.
    \item Showed ability to follow strict and specific guidelines from clients.
    \item Created custom webscrapers and data visualisations to independent businesses to help their growth.
    \item Showed ability to perform to a deadline.
  \end{resume_employer}
\end{resume_section}


\begin{resume_section}{Competitions and Personal Projects}
  \begin{resume_subsection}[(November 2018 & 2019)]{Hack Sussex}
  \begin{subitems}
    \item Worked with prestigious companies such as Rolls Royce to develop their product.
    \item Worked with multiple different pieces of new hardware including Raspberry Pi's and Arduinos to create a machine vision program - showing the ability to pick up new technologies.
    \item Learnt to work in a team environment, nurturing time and asset management skills.
    \item Had problem solving and critical thinking skills tested when working in a time pressure environment.
    \item Won an award for best use of hardware from the machine vision project.
    \item Lead a team to create a game using unity and C#. Created a beat detection algorithm and Spotify api integration into the game. 
    \item Won the award for most atmospheric project from a beat detection gamemode. 
    \end{subitems}
  \end{resume_subsection}

    \begin{resume_subsection}[(December 2017 - Current)]{Data science blog}
    \begin{subitems}
        \item Wrote multiple articles along with data visualisations about interesting topics.
        \item Dived into machine learning with Tensorflow using large datasets.
        \item Learned how to do webscrapes for websites with and without javascript elements.
        \item Improved writing skills by continuing to update the blog.
        \item Learned how to code aesthetically pleasing visualisations in seaborn and matplotlib.
    \end{subitems}
  \end{resume_subsection}
  

\begin{resume_section}{Education}
  \begin{resume_subsection}[Brighton (2018-Present)]{University of Sussex}
    \begin{subitems}
      \item Computer science and AI (With a year in industry)
      \item Achieved a first class degree in year 1.
    \end{subitems}
  \end{resume_subsection}
  
  
  \begin{resume_subsection}[Isle of Wight (2015-2018)]{Cowes Enterprise College Sixth Form}
    \begin{subitems}
      \item A-levels in: Psychology, maths and chemistry
      \item Results of: B, B, B
     \end{subitems}
  \end{resume_subsection}
\end{resume_section}

 \begin{resume_section}{Hobbies}
	\begin{subitems}
	 \item Snowboarding has been a great passion of mine for a few years, it has given me a break from studies as well as a creative outlet and a way to challenge myself.
	 \item Travelling to multiple places throughout the world has opened my eyes to not only new cultures but the joy for overcoming challenges and achieving goals even when seemingly impossible.
    \end{subitems}
  \end{resume_subsection}
\end{resume_section}
    
	


\end{document}! LaTeX Error: \begin{list} on input line 129 ended by \end{document}.See the LaTeX manual or LaTeX Companion for explanation.Type H <return> for immediate help.... \end{document}
